Galois Slicing as Differentiation

### 2025-07-11 main.tex
[ tex ] review mode
Typo.

\documentclass[acmsmall,screen,anonymous]{acmart}

@@

\begin{abstract}
  \GPS is a technique for program slicing for provenance, developed by
  Perera and collaborators. \GPS aims to explain program executions by
  demonstrating how to track approximations of the input and output
  forwards and backwards along a particular execution. In this paper,
  we explore a analogy between \GPS and differentiable programming,
  seeing the implementation of \GPS as a kind of automatic
  differentiation. Using the CHAD approach to automatic differentation
  due to V{\'a}k{\'a} and collaborators, we reformulate \GPS via a
  categorical semantics. In doing so, we are able to explore
  extensions of the \GPS idea to quantitative interval analysis, and
  to clarify the implicit choices made in existing \GPS
  instantiations.
\end{abstract}
\maketitle

>>>>

\documentclass[acmsmall,screen,anonymous,review]{acmart}

@@

\begin{abstract}
  \GPS is a technique for program slicing for provenance, developed by
  Perera and collaborators. \GPS aims to explain program executions by
  demonstrating how to track approximations of the input and output
  forwards and backwards along a particular execution. In this paper,
  we explore an analogy between \GPS and differentiable programming,
  seeing the implementation of forwards and backwards slicing as a kind of automatic
  differentiation. Using the CHAD approach to automatic differentation
  due to V{\'a}k{\'a}r and collaborators, we reformulate \GPS via a
  categorical semantics. In doing so, we are able to explore
  extensions of the \GPS idea to quantitative interval analysis, and
  to clarify the implicit choices made in existing instantiations of this approach.
\end{abstract}
\maketitle
